Calculating the Solvent Exposed Surface Area of Proteins with Intersecting Spheres

### 2020-06-07 Paper.tex
Edits

\subsection{Distance Preserving Motion}
In distance preserving motion, one sphere rotates around the other. Imagine three spheres interesting at two points, $p$ and $q$ (Figure 9). This time, $F$ is going to include all the points contained in all three spheres. It is assumed that if the spheres intersect at two points then one sphere contains the other two. In this case, it is $S_j$ that engulfs $S_i$ and $S_k$. The caps, or tops of the spheres, are considered. From a previous section, we know that $B_{ijk}$ is considered the line segment of three intersecting spheres. In this case, $B_{ijk}$ is the line segment containing $p$ and $q$. The caps $C_{ij} = B_i \cup S_j$ and $C_{kj} = B_k \cup S_j$ protrude from the surface of $S_j$. The parameters obtained from this diagram allows us to find the area similar to how we found it for the direction preserving motion. This model says that as you move the two caps apart, keeping their centers in the same position, you will gain an area equal to that of a spherical rectangle. Essentially, the caps are rotating in place. It might be easy to think about how diameter of the caps can represent the height of this “rectangle” while the distance between the caps signifies its width.
\begin{figure}[h!]
\caption{Three intersecting spheres at two points: $S_i$, $S_k$ and $S_j.\lbrack1\rbrack$}
\centerline{\includegraphics[width=3in]{Figure7}}
\end{figure}

@@

\section{Supplemental Information}
List of PDB's used: \\
1W4H, 2FD7, 1I2U, 1HA8, 1RO3, 1FRE, 1AHL, 1B8W, 1B7I, 3UA6,\\
1B7K, 1IVA, 1L6H, 1KTH, 2GQV, 2KXK, 1CDT, 1BF0, 1B7V, 4AEI,\\
4BWS, 1UBQ, 1FGP, 1CPZ, 1B4R, 1CRE, 2BCB, 4ZK9, 1BCG, 1B3C,\\
1G47, 1NEI, 1HYM, 1A7H, 1COU, 4W9A, 1A70, 1EMV, 1AVS, 1QYS,\\
1BB8, 1HA6, 2HSH, 2ACY, 1THX, 2Z9H, 2CBM, 2APB, 2FLS, 1AIU,\\
4DZN, 1SRR, 2GZV, 2XKH, 1RKI, 1BMG, 2MCT, 1FI5, 1WOU, 1DZO,\\
1DC9, 5PC4, 1WDV, 2OXZ, 1P3B, 129L, 4FH1, 1S2B, 2R32, 1BWR,\\
6MKL, 3CS1, 3PMD, 2O35, 3S9B, 3PFC, 2CA8, 2EBY, 1IIB, 1GAJ,\\
1I9Q, 4LUP, 3RQ8, 1VHI, 5OIL, 6CW0, 2YM4, 2ZO1, 4KXO, 6G0M,\\
5R2D, 2GNP, 6F65, 2CM8, 5OH3, 2W5L, 2VV9, 6CQS, 6DJA, 6D40.

>>>>

\subsection{Distance Preserving Motion}
In distance preserving motion, one sphere rotates around the other. Imagine three spheres interesting at two points, $p$ and $q$ (Figure 9). This time, $F$ is going to include all the points contained in all three spheres. It is assumed that if the spheres intersect at two points then one sphere contains the other two. In this case, it is $S_j$ that engulfs $S_i$ and $S_k$. The caps, or tops of the spheres, are considered. From a previous section, we know that $B_{ijk}$ is considered the line segment of three intersecting spheres. In this case, $B_{ijk}$ is the line segment containing $p$ and $q$. The caps $C_{ij} = B_i \cup S_j$ and $C_{kj} = B_k \cup S_j$ protrude from the surface of $S_j$. The parameters obtained from this diagram allows us to find the area similar to how we found it for the direction preserving motion. This model says that as you move the two caps apart, keeping their centers in the same position, you will gain an area equal to that of a spherical rectangle. Essentially, the caps are rotating in place. It might be easy to think about how diameter of the caps can represent the height of this “rectangle” while the distance between the caps signifies its width.
\begin{figure}[h!]
\caption{Three intersecting spheres at two points: $S_i$, $S_k$ and $S_j$.\cite{Bryant}}
\centerline{\includegraphics[width=3in]{Figure7}}
\end{figure}

@@

\section{Supplemental Information}
List of PDB's used: \\
129L, 1A70, 1A7H, 1AHL, 1AIU, 1AVS, 1B3C, 1B4R, 1B7I, 1B7K,\\
1B7V, 1B8W, 1BB8, 1BCG, 1BF0, 1BMG, 1BWR, 1CDT, 1COU, 1CPZ,\\
1CRE, 1DC9, 1DZO, 1EMV, 1FGP, 1FI5, 1FRE, 1G47, 1GAJ, 1HA6,\\
1HA8, 1HYM, 1I2U, 1I9Q, 1IIB, 1IVA, 1KTH, 1L6H, 1NEI, 1P3B,\\
1QYS, 1RKI, 1RO3, 1S2B, 1SRR, 1THX, 1UBQ, 1VHI, 1W4H, 1WDV,\\
1WOU, 2ACY, 2APB, 2BCB, 2CA8, 2CBM, 2CM8, 2EBY, 2FD7, 2FLS,\\
2GNP, 2GQV, 2GZV, 2HSH, 2KXK, 2MCT, 2O35, 2OXZ, 2R32, 2VV9,\\
2W5L, 2XKH, 2YM4, 2Z9H, 2ZO1, 3CS1, 3PFC, 3PMD, 3RQ8, 3S9B,\\
3UA6, 4AEI, 4BWS, 4DZN, 4FH1, 4KXO, 4LUP, 4W9A, 4ZK9, 5OH3,\\
5OIL, 5PC4, 5R2D, 6CQS, 6CW0, 6D40, 6DJA, 6F65, 6G0M, 6MKL.
